Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

Specifically, we (adversarially) train imagenet-initialized ResNet-18
(RN18)~\cite{resnet} with the output dimension of the last layer changed to
$N=512$.
%
The margin $\gamma$ in triplet loss is $0.2$ by default.
%
Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
as $1.0\times 10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.

For adversarial training, we adopt the perturbation budget of
$\varepsilon=8/255$ in infinity norm ($p=\infty$).
%
Projected Gradient Descent (PGD)~\cite{madry} is used for creating adversarial
examples, with a maximum step number set as $\eta=8$ by default.\footnote{
Instead of $\eta=32$ as in \cite{robrank} in order to control time consumption.}
%
Step size for PGD is set as $\alpha=1/255$.
%
The setup is also consistent to standard DML~\cite{revisiting}.

The model performance on benign (\ie, unperturbed) examples is measured in
Recall@1 (R@1), Recall@2 (R@2), mAP and NMI
following~\cite{revisiting,robrank}.
%
The adversarial robustness of a model is measured in Empirical Robustness Score
(ERS)~\cite{robrank}, which is a normalized score (the higher the better) from
an ensemble of existing white-box attacks against DML or their simplified
white-box counterparts.
%
As adversarial training will not cause gradient masking~\cite{obfuscated},
the performance of white-box attack can be regarded as the upper bound of the
corresponding black-box attack.
%
An adversarially trained DML model that is empirically robust to the ensemble
is expected to be robust in other scenarios as well.

\oo{Concretely, the ensemble of attack for computing ERS includes.}

>>>>

Specifically, we (adversarially) train imagenet-initialized ResNet-18
(RN18)~\cite{resnet} with the output dimension of the last layer changed to
$N{=}512$.
%
The margin $\gamma$ in triplet loss is $0.2$ by default.
%
The setup is also consistent to standard DML~\cite{revisiting}.
%
Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
as $1.0{\times}10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
%
Adversarial examples are created under the perturbation budget
$\varepsilon{=}8/255$ in infinity norm, using the
Projected Gradient Descent (PGD)~\cite{madry} method with step size $\alpha{=}1/255$ 
and a default maximum step number $\eta{=}8$.
%

The model performance on benign (\ie, unperturbed) examples is measured in
Recall@1 (R@1), Recall@2 (R@2), mAP and NMI
following~\cite{revisiting,robrank}.
%
The adversarial robustness of a model is measured in Empirical Robustness Score
(ERS)~\cite{robrank}, a normalized score (the higher the better) from
an ensemble of existing attacks against DML or their simplified white-box
alternatives.
%
Since adversarial training is not gradient masking~\cite{obfuscated}, the
performance of white-box attack can be regarded as the upper bound of the
black-box attacks, and thus a model that is empirically robust to the ensemble
of white-box attacks is expected to be robust in general.

\oo{Concretely, the ensemble of attack for computing ERS includes.}
%
Further details can be found in the supplementary.
